\begin{question}
  Some authors define an operator to be real when every member of its
  matrix elements $\mel{b'}{A}{b''}$ is real in some representation
  ($\{\ket{b'}\}$ basis in this case).  Is this concept representation
  independent, that is, do the matrix elements remain real even if
  some basis other than $\{\ket{b'}\}$ is used? Check your assertion
  using familiar operators such as $S_y$ and $S_z$ (see Problem
  \ref{1.26:theQuestion}) or $x$ and $p_x$.
\end{question}

\begin{purpose}
  My trusty cyber-TA says that the purpose of this problem is to drive
  home that things like ``Hermitian'' are intrinsic to the operator
  whereas the matrix representations are pretty tightly-coupled to the
  basis in which they are expressed... because... duh since the
  definition of those entries includes $\mel{a_i}{\hat{O}}{a_j}$.  I
  didn't find this one to be terribly deep.  Like and subscribe and
  leave a comment if you see a better way to handle this one.
\end{purpose}

\begin{answer}
  So, this one is pretty trivial to show that the answer is ``No''.
  Let's just start with a simple counter-example.

  \begin{equation}
    \begin{alignedat}{3}
      & x_1 &= \begin{bmatrix}1\\0\end{bmatrix}
        &
        \quad
        & x_2 &= \begin{bmatrix}0\\i\end{bmatrix}
          \\
      & y_1 &= \begin{bmatrix}1\\0\end{bmatrix}
        &
        \quad
        & y_2 &= \begin{bmatrix}0\\1\end{bmatrix}
          \\
    \end{alignedat}
  \end{equation}

  Now we consider the following two scenarios, of which only one can
  be true at a time.

  \begin{equation}
    \begin{split}
    \mel{x_1}{A}{x_2} &= \braket{x_1}{x_a} \in \mathbb{R}\\
    \mel{y_1}{A}{y_2} &= \braket{y_1}{y_a} \in \mathbb{R}\\
    \end{split}
  \end{equation}

  For the result to be entirely real, then the operator $A$ must
  modify $x_2$ to be entirely real when acted upon to become $x_a$.
  If $A$ does so (and produces a non-negative result) then using $y_1$
  and $y_2$ will produce a complex result.  He wanted us to talk about
  the spin operators so, expressing $S_y$ in the $\ket{y\pm}$ basis

  \begin{equation}
    S_y \dot{=} \frac{\hbar}{2}\begin{pmatrix}1&0\\0&-1\\\end{pmatrix}
  \end{equation}

  Like I explained to my kid, $10$ is always $N$ in base-N.
  Expressing it in the $\ket{z\pm}$ basis, gets us a purely imaginary
  result.  I guess that's what he's looking for with the callback to
  \ref{1.26:theQuestion}??

  We can also make it unreal pretty easily by application of phasors.
  Let's say we add a phasor of $e^{i\theta}$ to any of the basis
  vectors and call it a new basis.  Its presence won't change whether
  or not the new basis is orthogonal, but it will make one of the
  members complex.

  I'm not sure what he's going for here, but it's laughably simple to
  make these things blow up... maybe that's the (very simple)
  lesson???
\end{answer}
