\def\ctrois{C\'{o}mmute \`{a} Trois}

\begin{question}
  
Two observables $A1$ and $A2$, which do not involve time explicitly,
are known not to commute,

\begin{equation*}
  [A1 , A2] \ne 0,
\end{equation*}

yet we also know that $A1$ and $A2$ both commute with the Hamiltonian:

\begin{equation*}
  [A1, H] = 0, [A2, H] = 0.
\end{equation*}

\begin{questionpart}
  Prove that the energy eigenstates are, in general, degenerate.
\end{questionpart}

\begin{questionpart}
  Are there exceptions?
\end{questionpart}

\begin{questionpart}
  As an example, you may think of the central-force problem $H =
  \vb{p}^2/2m + V(r)$, with $A1 \rightarrow L_z$, $A2
  \rightarrow L_x$.
\end{questionpart}

\end{question}

\begin{purpose}

  OK, this problem is meant to be our first foray into wave mechanics
  and there are a LOT of things going on here.  I fell flat on my face
  the first time I tried to attempt this one until some external help
  allowed me to perform a rectal craniotomy and muddle through it.
  Let's start by listing a few of the things going on here:

  \begin{itemize}

  \item A simplistic view is to consider that $\hat{p} \equiv \left(
    -i \hbar \frac{\partial}{\partial x}\right)$.  As Sakurai
    discusses, working from the foundation of Hamltonian mechanics
    found in Goldstein, Sakurai posits the existence of a momentum
    operator $\hat{p}$ and then shows how it must behave.  In doing
    so, he develops a generalized expression of that behavior in
    equation 1.249.

  \item There is a difference between an abstract operator, say
    $\hat{p}$, and the expression of that operator in an integral.
    Considering the example of $\hat{p}$ when acting on a ket holding
    the position, the proper expression in physical space is $-i \hbar
    \left(\frac{\partial}{\partial x}\right)$ (well, more properly
    it's $-i \hbar \nabla \vb{x}$, and even more properly
    there's the expression for $\mel{x}{p}{\alpha}$) but if you're
    acting on a ket that represents the momentum, then it gets much
    more complicated and becomes $p$, if you're operating on a ket
    that represents Schr\"{o}dinger's cat (the sadist...who kills
    kittens!?) then I'm pretty sure it spontaneously generates a black
    hole.

  \item It's probably worth reviewing Goldstein chapter XXX where he
    derives the generators from Hamiltonian mechanics.

  \item The dimensionality of the infinities of eigenkets is equal to
    the number of times you find an eigenvalue.  Find $\lambda$ once?
    You have the typical line of eigenvectors (though we typically
    normalize to magnitude 1).  Twice?  You have a plane in which any
    two orthogonal vectors count as eigenvectors with the same
    eigenvalues as before.  Thrice?  you have a 3D space, and so on.

  \end{itemize}
\end{purpose}

\begin{answer}

  \begin{answerpart}{\ctrois{}}
    For simplicity and laziness, because I hate writing subscripts
    unnecessarily, I'm going to make a quick substitution:

    \begin{equation}
      \text{let }A_1 \equiv A, A_2 \equiv B
    \end{equation}

    Next, let's have a brief recitation of the problem setup:
    
    \begin{equation}
      \begin{split}
        &[A, B] = AB - BA \ne 0\\
        &[A, H] = AH - HA = [B, H] = BH - HB = 0\\
        &H = \sum_i h_i\Lambda_{h,i} + \sum_j h_d\Lambda_{h,d,j}\\
      \end{split}
    \end{equation}

    We know from problem FIXME that two operators commute if and only
    if they have a simultaneous eigenbasis.  So if they don't commute,
    they don't have a simultaneous eigenbasis.  That means we can
    rewrite our operators as follows.

    \begin{equation}
      \begin{split}
        A &= \sum_i a_{s,i}\Lambda_{s,i} + \sum_j a_{p,j}\Lambda_{a,p,j}
        = A_s + A_p\\
        B &= \sum_i b_{s,i}\Lambda_{s,i} + \sum_j b_{p,j}\Lambda_{b,p,j}
        = B_s + B_p\\
        H &= \sum_i h_{s,i}\Lambda_{s,i} + \sum_j h_{p,j}\Lambda_{h,p,j}
        = H_s + H_p\\
      \end{split}
    \end{equation}

    Here we use $s$ for the (s)hared eigenbasis and $p$ for the
    (p)rivate eigenbasis for that operator.  For simplicity, we have
    also broken out the shared vs private portions into their own
    operators $X_s$ and $X_p$.  So, we know that if there's a shared
    eigenbasis, it'll commute, and otherwise it won't, so that leaves:

    \begin{equation}
      \begin{split}
        [A, B]
        &= (A_s + A_p)(B_s + B_p) - (B_s + B_p)(A_s + A_p)\\
        &= (A_sB_s + A_sB_p + A_pB_s + A_pB_p)
        - (B_sA_s + B_sA_p + B_pA_s + B_pA_p)\\
      \end{split}
    \end{equation}

    We know that all the interior eigenbases are orthogonal, which
    allows us to eliminate cross-terms:
    \begin{equation}
      \begin{split}
        XY
        =\ &X_sY_s + X_sY_p + X_pY_s + X_pY_p\\
        =\ &(\sum_i x_{s,i}\Lambda_{s,i})(\sum_i y_{s,i}\Lambda_{s,i})\\
        &+ (\sum_i x_{s,i}\Lambda_{s,i})(\sum_i y_{p,i}\Lambda_{y,p,i})\\
        &+ (\sum_i x_{p,i}\Lambda_{x,p,i})(\sum_i y_{s,i}\Lambda_{s,i})\\
        &+ (\sum_i x_{p,i}\Lambda_{x,p,i})(\sum_i y_{p,i}\Lambda_{y,p,i})\\
        =\ &\sum_i x_{s,i}y_{s,i}\Lambda_{s,i}
        + (\sum_i x_{p,i}\Lambda_{x,p,i})(\sum_i y_{p,i}\Lambda_{y,p,i})\\
        =\ &X_sY_s + X_pY_p\\
      \end{split}
    \end{equation}

    Expanding to the full commutation:

    \begin{equation}
      \begin{split}
        [A, B]
        &= (A_sB_s + A_pB_p) - (B_sA_s + B_pA_p)\\
        &= (A_sB_s - B_sA_s) + (A_pB_p - B_pA_p)\\
        &= [A_s,B_s] + [A_p, B_p]\\
      \end{split}
    \end{equation}

    Since, by definition, the $X_s$ portions have a shared eigenbasis,
    we already know that the commutation goes to 0, which leaves us with:
    
    \begin{equation}
      \begin{split}
        [A, B]
        &= [A_s,B_s] + [A_p, B_p]\\
        &= [A_p, B_p]\\
      \end{split}
    \end{equation}

    We can use the same logic with $A$ and $B$ when they commute with
    $H$:

    \begin{equation}
      \begin{split}
        [X, H]
        &= [X_s,H_s] + [X_p, H_p]\\
        &= [X_p, H_p]\\
        &= 0\\
      \end{split}
    \end{equation}

    Since commutation means simultaneous eigenbasis, that also means
    that there must exist an eigenbasis that works for both operators.

    \begin{equation}
      \begin{split}
        &\exists \left\{\Lambda_{h,a,i}\right\} \text{ s.t.}\\
        & H = H_s + \sum_i h_{a,i}\Lambda_{h,a,i}\\
        & A = A_s + \sum_i a_{h,i}\Lambda_{h,a,i}\\
        \Rightarrow & \sum_i h_{a,i}\Lambda_{h,a,i} = \sum_i h_{i}\Lambda_{h,i}\\
      \end{split}
    \end{equation}

    %% So now we're talking about having \emph{multiple} sets of
    %% eigenkets that work for $A/B$ or $H$ or both.  When you hear that,
    %% your degeneracy senses should start tingling.  Now that we know we
    %% can express our $A/H$ shared kets using $H$'s original kets, we
    %% know that they both occupy the same space.  We can make use of
    %% another property to write that:

    %% \begin{equation}
    %%   \begin{split}
    %%     I
    %%     &= \sum_i \Lambda_{s,i} + \sum_j \Lambda_{h,j}\\
    %%     &= \sum_i \Lambda_{s,i} + \sum_j \Lambda_{a,j}\\
    %%     &= \sum_i \Lambda_{s,i} + \sum_j \Lambda_{b,j}\\
    %%     &= \sum_i \Lambda_{s,i} + \sum_j \Lambda_{h,a,j}\\
    %%     &= \sum_i \Lambda_{s,i} + \sum_j \Lambda_{h,b,j}\\
    %%   \end{split}
    %% \end{equation}
    
    %% That's a whole lotta sums so lemme sum it up for you.  They're all
    %% eigenbases, so the projection operators all sum to the identity
    %% matrix.  We can also remove the shared eigenkets to show that:

    %% \begin{equation}
    %%     \sum_j \Lambda_{h,j}
    %%     = \sum_j \Lambda_{a,j}
    %%     = \sum_j \Lambda_{b,j}
    %%     = \sum_j \Lambda_{h,a,j}
    %%     = \sum_j \Lambda_{h,b,j}
    %% \end{equation}
    
    So, it's easy to show that $A$ and $B$ don't commute simply by
    postulating that they don't share a simultaneous eigenbasis.  The
    fun part is showing that with the shared vs private
    parameterization of the operators, $A/B$ and $H$ \emph{do}
    commute.
    
    With the completeness theorem, we know that the sum of the
    projectors is $I$ and we know that we can build our new
    simultaneous basis using the original basis kets.  The trick of it
    is that the new simultaneous basis will also need to be an
    eigenbasis, which means it'll need to obey the core eigenvalue
    equation:

    \begin{equation}
      \begin{split}
        k_i \ket{h,a,i}
        &= \hat{H}_p \ket{h,a,i}\\
        &=
        \Bigg(\sum_j h_{p,j}\Lambda_{h,p,j}\Bigg)
        \ket{h,a,i}
        \\
        &=
        \Bigg(\sum_j h_{p,j}\Lambda_{h,p,j}\Bigg)
        \Bigg(\sum_k c_{a,i,k} \ket{h,p,k}\Bigg)
        \\
        &=
        \sum_j \sum_k
        h_{p,j}\Lambda_{h,p,j}
        c_{a,i,k} \ket{h,p,k}
        \delta_{jk}
        \\
        &= \sum_k h_{p,k} c_{a,i,k} \ket{h,p,k}\\
      \end{split}
    \end{equation}

    This one could use some explanation.  $\ket{h,a,i}$ is the
    eigenket for the $\hat{H}_p$ operator that has been adjusted to
    play nicely with the $A$ operator and it's the $i$th such ket.
    $h_{p,j}$ is the $j$th eigenvalue of the $\hat{H}_p$ (which as a
    reminder is the unshared subspace of the $\hat{H}$ operator).
    $c_{a,i,k}$ is the projection coefficient to produce the $i$th
    simultaneous basis vector in the $\hat{H}_p$ operator drawing upon
    the $k$th traditional eigenvector all to play nicely with the
    $\hat{A}_p$ operator.  If we clean that up a bit and scope it to
    the interaction between $\hat{H}_p$ and $\hat{A}_p$, then we get:

    \begin{equation}
      \begin{split}
        k_i \ket{a_i}
        &= \hat{H} \ket{a_i}\\
        &=
        \Bigg(\sum_j h_{j}\Lambda_{h,j}\Bigg)
        \ket{a_i}
        \\
        &=
        \Bigg(\sum_j h_{j}\Lambda_{h,j}\Bigg)
        \Bigg(\sum_k c_{k} \ket{h,k}\Bigg)
        \\
        &=
        \sum_j \sum_k
        h_{j}\Lambda_{h,j}
        c_{k} \ket{h,k}
        \delta_{jk}
        \\
        &= \sum_k h_{k} c_{k} \ket{h,k}\\
        \Rightarrow
        \sum_k k_{i} c_{k} \ket{h,k}
        &= \sum_k h_{k} c_{k} \ket{h,k}\\
        \Rightarrow
        k_{i} &= h_{k} = h_d\\
      \end{split}
    \end{equation}

    For the above relation to hold then $\forall i, h_k = k_i$ which
    implies that $h_k$ is shared amongst all of the kets as a single
    constant.  We can easily calculate the value by assigning $c_1 =
    1$ (implying the others are 0) whereupon we see that the resulting
    value must be $h_d$ since it's just the same as the original
    degenerate eigenvector and so the eigenvalue will be the same as
    well.

    This is the part where the observant reader (or annoying ai
    assistant) might point out that the problem \emph{technically}
    doesn't require that you prove that the \ctrois{} is
    \emph{possible} with degeneracy\ldots rather, it just asks that
    you show that \emph{if} it's true, then degeneracy is
    involved... So here, for your very brief pleasure, is the short
    version:

    If $\forall i \lambda_{h,i} \ne \lambda_{h,j \ne i}$ then $H =
    H_s$.  If $[A, H] = 0$, then $A = A_s$.  Since the same can be
    said of $B$ then it means that all three operators share the same
    eigenbasis and they would all commute.  So, clearly, $H \ne H_s$.

    That's it...that's all it was asking for... ::sigh::
  \end{answerpart}

  \begin{answerpart}{Exceptions}
    So, in general, the proof hinges upon the degenerate
    subspace($\hat{H}_d$) encompassing the private subspace
    ($\hat{A}_p$ and $\hat{B}_p$) of the other operators.

    \begin{equation}
      \begin{split}
        [A, B] &= [A_p, B_p] \ne 0\\
        [A, H] &= [A_p, H_p] = 0\\
        [B, H] &= [B_p, H_p] = 0\\
      \end{split}
    \end{equation}

    So, any edge-cases which meet the above restrictions will work.
    The most obvious is if $H_p = 0$.  However, if we do that, we're
    also introducing a degeneracy since the eigenvalues are all
    trivially $0$ which would \emph{technically} not be an exception.

    Next we explore the concept of having one eigenvalue in each of
    two matrices that don't fully share an eigenbasis be
    0...unfortunately, that doesn't work either.  You need a minimum
    of two eigenvectors to be different (since all eigenvectors are
    orthogonal, you can't just randomly reorient the last one, you
    have to reorient a minimum of two of them).  That means that the
    minimum dimensionality for $\hat{X}_p$ is 2 which means that when
    you look at the commutation of, say $\hat{H}_p$ and $\hat{B}_p$
    (let's assume you've delcared that $\hat{H}$ and $\hat{A}$ share
    an eigenbasis), then you get

    \begin{equation}
      \begin{split}
        [\hat{H}, \hat{B}]
        &= (h_1\Lambda_{h,1} + h_2\Lambda_{h,2})
        (b_1\Lambda_{b,1} + b_2\Lambda_{b,2})
        - (b_1\Lambda_{b,1} + b_2\Lambda_{b,2})
        (h_1\Lambda_{h,1} + h_2\Lambda_{h,2})\\
        &= (
        h_1b_1\Lambda_{h,1}\Lambda_{b,1}
        + h_1b_2\Lambda_{h,1}\Lambda_{b,2}
        + h_2b_1\Lambda_{h,2}\Lambda_{b,1}
        + h_2b_2\Lambda_{h,2}\Lambda_{b,2})\\
        &\ \ - (
        h_1b_1\Lambda_{b,1}\Lambda_{h,1}
        + h_1b_2\Lambda_{b,1}\Lambda_{h,2}
        + h_2b_1\Lambda_{b,2}\Lambda_{h,1}
        + h_2b_2\Lambda_{b,2}\Lambda_{h,2})\\
      \end{split}
    \end{equation}

    As you can see, though, there is no combination of $h_i$, $b_i$,
    $\Lambda_{h,i}$, or $\Lambda_{b,i}$ where you can zero out a
    single item from each matrix that will allow it to commute
    cleanly.  That means that if you want to zero it out, you're gonna
    need degeneracy.

    That being said...it was pointed out to me...annoyingly...that
    Sakurai doesn't want us to show that it's true in general, only
    that there exists an exceptional \emph{eigenstate} which, when
    acted upon by the commutation operators, violates the \ctrois{}.

    So if we dive in, then there's at least one obvious counterexample
    which is the null ket ($\ket{0}$).  This one obviously violates
    the \ctrois{} because $[\hat{A}, \hat{B}]\ket{0} = \ket{0}$.  That
    being said, there are a couple of problems here.  First off, in
    the world of quantum mechanics, zero energy (though technically
    any energy value would be mathematically consistent there, but 0
    seems most appropriate to consider) isn't really a thing...unless
    there, well, isn't anything...but we haven't really gotten to that
    in the book yet.

    Speaking of $0$ energy...that would mean that you have $0$
    momentum (or negative potential) which would run afoul of the
    $[\hat{p}, \hat{x}]$ uncertainty essentially turning this into the
    world's biggest Bose occupying, well, everywhere; but again...we
    haven't covered that yet.

    The final problem is that \emph{teeeeechnically} speaking,
    $\ket{0}$ cannot be considered an eigenket because by
    \emph{convention} we don't consider the $0$ vector to be an
    eigenvector.

    That leaves us with two final counterexamples which don't violate
    any of the rules.  First, we consider the case where you have an
    eigenstate within the null space of $[\hat{A}, \hat{B}]$.  That
    would violate the \ctrois{} because the $[\hat{A}, \hat{B}]$
    commutation works out to $0$.  The problem states that they are
    ``known not to commute'' so this one qualifies as an exception.

    That leaves us with one final counterexample: if you set
    $\hat{H}_p = \hat{A}_p \ne \hat{B}_p$ and place the energy
    eigenstate in the nullspace of $[\hat{B}, \hat{H}]$ then you could
    preserve the \ctrois{}, but without the degeneracy that is
    mandated in the general case.  The problem setup is $[\hat{A},
      \hat{B}] \ne \hat{0}$ and $[\hat{A}, \hat{H}] = [\hat{B},
      \hat{H}] = \hat{0}$ \emph{and} that there is degeneracy in the
    Hamiltonian.  This counterexample allows us to maintain the
    commutation relations \emph{without} the degeneracy.
  \end{answerpart}

  \begin{answerpart}{T+V Example}
    now we're examining orbital angular momentum with $A \equiv L_z$
    and $B \equiv L_x$.

    According to the intertubes:
    \begin{equation}
      \begin{split}
        \{L_i, L_j\} &= L_k \epsilon_{ijk}\\
        \{L_i, H\} &= 0\\
      \end{split}
    \end{equation}

    Drawing upon the wisdom of the book:
    \begin{equation}
      \tag{1.229}
      [\ ,\ ]_{\text{classical}} \rightarrow \frac{[\ ,\ ]_{\text{}}}{i\hbar}
    \end{equation}

    Combining those, we see that

    \begin{equation}
      [L_i, H] = i\hbar \cdot 0
    \end{equation}

    \begin{equation}
      [L_z, L_x] = i\hbar L_y \ne 0
    \end{equation}

    So, the conditions of the problem are clearly met in this case.
    We can also clearly see that there must be degeneracy because the
    state vector includes position and the amount of energy is a
    function only of the radius $r$ and not of the specific
    coordinates, so any set of coordinates which share the same radius
    will share the same energy.  We can also draw upon both classical
    physics and a quantum mechanical theorem not covered in this
    chapter (the Virial theorem) to show that we can't reallocate
    energy from $T$ and place it in $V$ instead.

    The Virial theorem\incite{wikipediaVirial} states that:
    \begin{equation}
      \ev{T} = - \frac{1}{2} \sum_{k=1}^{N}\ev{\vb{F}_k \cdot \vb{r}_k}
    \end{equation}

    As we can see, the kinetic is just as bound by the radius as the
    potential.

  \end{answerpart}

\end{answer}
