\begin{question}

  \begin{questionpart}
    Starting with a momentum operator $\vb{p}$ having eigenstates
    $\ket{\vb{p}'}$, define an infinitesimal boost operator
    $\mathscr{B}(d\vb{p}')$ that changes one momentum eigenstate into
    another, that is

    \begin{equation*}
      \mathscr{B}(d\vb{p}')\ket{\vb{p}'} = \ket{\vb{p}' + d\vb{p}'}
    \end{equation*}
  \end{questionpart}

  \begin{questionpart}
    Show that the form $\mathscr{B}(d\vb{p}') = 1 + i\vb{W}\cdot
    d\vb{p}'$, where W is Hermitian, satisfies the unitary,
    associative, and inverse properties that are appropriate for
    $\mathscr{B}(d\vb{p}')$.
  \end{questionpart}

  \begin{questionpart}
    Use dimensional analysis to express $\vb{W}$ in terms of the
    position operator $\vb{x}$, and show that the result satisfies the
    canonical commutation relations $[x_i,p_j] = -i\hbar\delta_{ij}$.
  \end{questionpart}

  \begin{questionpart}
    Derive an expression for the matrix element
    $\mel{\vb{p}'}{\vb{x}}{\alpha}$ in terms of a derivative with
    respect to $\vb{p}'$ of $\braket{\vb{p}'}{\alpha}$.
  \end{questionpart}
\end{question}

\begin{purpose}
  We actually saw (what I call) the ``Jerk'' operator way back in
  problem \ref{1.36.b:theAnswer}, but he wants us to fully explore the
  derivation, usage, and properties of it which seems like fun.
\end{purpose}

\begin{answer}

  \begin{answerpart}{Make it So}
    Sakurai actually does a lot of the work for this problem.  He
    spends a solid 10 pages developing the $\mathscr{J}$ operator
    which is going to play a key role.  Most of that derivation is
    entirely applicable to this problem.  For example, all of \S1.6.3
    appears to be directly applicable with the change from $x
    \rightarrow p$.  Adding two boosts ($dp'$ and $dp''$) should
    result in $\ket{p + dp' + dp''}$ and the order of those additions
    shouldn't matter to the final momentum.  Adding then removing
    momentum should be like it never happened so the inverse is the
    negative is the hermitian conjugate.  Momentum is differentiable
    so the first-order linear approximation at infinitesimal distances
    is still rigorous, etc.  These properties are all prety
    straight-forward.

    It's worth noting that the form of the operator ansatzed by
    Sakurai is

    \begin{equation}
      \tag{1.202}
      \mathscr{J}(d\vb{x}') = 1 - i\vb{K} \cdot d\vb{x}'
    \end{equation}

    Pulling in the equation that goes from the infinitesimal boost to
    the macroscopic boost

    \begin{equation}
      \inlabel{theKey}
      \tag{1.218}
      \begin{split}
        \mathscr{J}(\Delta x'\vb{\hat{x}})
        &= \lim_{N \rightarrow \infty}
        \left(
        1 - \frac{ip_x\Delta x'}{N\hbar}
        \right)^N
        \\
        &= \exp
        \left(
        -\frac{ip_x\Delta x'}{\hbar}
        \right)
        \\
      \end{split}
    \end{equation}

    Applying those equations to our case, where the existing logic
    still holds and we get

    \begin{equation}
      \begin{split}
        \mathscr{B}(\Delta p'\vb{\hat{p}})
        &= \lim_{N \rightarrow \infty}
        \left(
        1 - \frac{i\vb{k}\Delta p'}{N}
        \right)^N
        \\
        &= \exp
        \left(
        -i\vb{k}\Delta p'
        \right)
        \\
      \end{split}
    \end{equation}

    So, we've ansatz'd the form and now we're looking for a way to
    solve for $k$, then we're going to have to use the established
    relationship between position and momentum.  The development of
    the momentum operator comes from use of momentum as a generator of
    translation and isn't even fully derived here, but rather calls
    out to Goldstein (see equation 1.211).  Obviously, that isn't
    going to work for us.  We're probably going to have to use
    uncertainty relations, so let's see wht happens.

    \begin{equation}
      \begin{alignedat}{2}
        &&[\vb{p}, \mathscr{B}(\dd{\vb{p}''})]\ket{\alpha}
        &= (\vb{p}\mathscr{B}(\dd{\vb{p}''}) - \mathscr{B}(\dd{\vb{p}''})\vb{p})\ket{\alpha}\\
        &&&= \vb{p}\mathscr{B}(\dd{\vb{p}''})\ket{\alpha} - \mathscr{B}(\dd{\vb{p}''})\vb{p}\ket{\alpha}\\
        &&&=
        \int \dd{\vb{p}'} \vb{p}\mathscr{B}(\dd{\vb{p}''})\ket{\vb{p}'}\braket{\vb{p}'}{\alpha}
        - \mathscr{B}(\dd{\vb{p'}})\vb{p}\ket{\vb{p}'}\braket{\vb{p}'}{\alpha}
        \\
        &&&=
        \int \dd{\vb{p}'} \vb{p}\ket{\vb{p}' + \dd{\vb{p}''}}\braket{\vb{p}'}{\alpha}
        - \vb{p}'\mathscr{B}(\dd{\vb{p}''})\ket{\vb{p}'}\braket{\vb{p}'}{\alpha}
        \\
        &&&=
        \int \dd{\vb{p}'} (\vb{p}' + \dd{\vb{p}''})\ket{\vb{p}' + \dd{\vb{p}''}}\braket{\vb{p}'}{\alpha}
        - \vb{p}'\ket{\vb{p}' + \dd{\vb{p}''}}\braket{\vb{p}'}{\alpha}
        \\
        &&&=
        \int \dd{\vb{p}'}
        ((\vb{p}' + \dd{\vb{p}''}) - \vb{p}')
        \ket{\vb{p}' + \dd{\vb{p}''}}
        \braket{\vb{p}'}{\alpha}
        \\
        &&&=
        \int \dd{\vb{p}'}
        \dd{\vb{p}''}
        \ket{\vb{p}' + \dd{\vb{p}''}}
        \braket{\vb{p}'}{\alpha}
        \\
        &&&=
        \dd{\vb{p}''}
        \int \dd{\vb{p}'}
        \mathscr{B}(\dd{\vb{p''}})
        \ket{\vb{p}'}
        \braket{\vb{p}'}{\alpha}
        \\
        &&&=
        \dd{\vb{p}''}
        \mathscr{B}(\dd{\vb{p''}})\ket{\alpha}
        \\
      \end{alignedat}
    \end{equation}

    OK, so now we've found a difference between what we did and what
    the book does.  Unlike equation 1.207 from the book, we see that

    \begin{equation}
      [\vb{p}, \mathscr{B}(\dd{\vb{p'}})] =
      \dd{\vb{p'}}\mathscr{B}(\dd{\vb{p'}})
    \end{equation}

    So where did we go off the rails?  well... it turns out that we
    didn't.  The book is... well... the book is
    wrong... OK... teeeechhnically it's right... he just plays it a
    little fast-and-loose with a couple of worthy details.  So let's
    dig into this one shall we?  The book says this:

    \begin{equation}
      \tag{1.207}
      [\vb{x}, \mathscr{J}(\dd{\vb{x}'})] = \dd{\vb{x}'}
    \end{equation}

    But, exactly the same logic and mechanism applies.  If you really
    want, you can copy/paste and s/p/x/g\footnote{If you don't know
    sed then we probably won't be friends.} if you want, but I don't
    think that's worth taking up valuable space in this manual which
    was clearly written to be constrained to a maximum page-count (he
    writes, sarcastically).  So why does Sakurai do this?  Look at
    equation 1.201

    \begin{equation}
      \tag{1.201}
      \lim_{d\vb{x}' \rightarrow 0}\mathscr{J}(d\vb{x}') = 1
    \end{equation}

    He's relying upon the usage of the jog operator with a complete
    differential vs when employing it on a more macroscopic $\Delta
    \vb{x}'$.  It's worth noting that the exact same logic applies to
    the $\mathscr{B}$ operator since it, too, is constructed with $1 -
    \vb{k}\cdot\vb{\dd{p}}'$ so the same limitting process applies.
    OK, back to our regularly-scheduled pain.

    We worked out the commutation, but that didn't really get us
    anywhere so let's abandon that line of reasoning and try something
    else.  Let's see what happens when we try to work out the $[x,B]$
    commutation.  We'll start by working out the $xB\ket{\alpha}$
    part

    \begin{equation}
      \begin{alignedat}{2}
        && \vb{x}\mathscr{B}(\Delta \vb{p}')\ket{\alpha}
        &=
        \iiint \dd{\vb{x}'} \dd{\vb{x}''} \dd{\vb{p}'}
        \vb{x}
        \Lambda_{x'}
        \mathscr{B}(\dd{\vb{p}}) \Lambda_{p'}
        \Lambda_{x''}
        \ket{\alpha}
        \\
      \end{alignedat}
    \end{equation}

    So, all we've done so far is to multiply by $\hat{1}$ a few times
    using the completeness relation.
    
    \begin{equation}
      \begin{alignedat}{2}
        && \vb{x}\mathscr{B}(\Delta \vb{p}')\ket{\alpha}
        &=
        \iiint \dd{\vb{x}'} \dd{\vb{x}''} \dd{\vb{p}'}
        \vb{x}
        \Lambda_{x'}
        \mathscr{B}(\Delta \vb{p}') \Lambda_{p'}
        \Lambda_{x''}
        \ket{\alpha}
        \\
        &&&=
        \iiint \dd{\vb{x}'} \dd{\vb{x}''} \dd{\vb{p}'}
        \vb{x}
        \ket{\vb{x}'}
        \underbrace{\braket{\vb{x}'}{p' + \Delta \vb{p}'}}_{\text{eq 1.264}}
        \underbrace{\braket{p'}{\vb{x}''}}_{\text{eq 1.264}^{*}}
        \braket{\vb{x}''}{\alpha}
        \\
      \end{alignedat}
    \end{equation}

    Pulling in equation 1.264 which was developed using the formalism
    of the $\mathscr{J}$ operator and not the $\mathscr{B}$ operator

    \begin{equation}
      \inlabel{xp}
      \tag{1.264}
      \braket{x'}{p'} =
      \frac{1}{\sqrt{2\pi\hbar}}
      \exp(\frac{ip'x'}{\hbar})
    \end{equation}

    Applying that equation to our double integral

    \begin{equation}
      \begin{alignedat}{2}
        && \vb{x}\mathscr{B}(\Delta \vb{p}')\ket{\alpha}
        &=
        \iiint \dd{\vb{x}'} \dd{\vb{x}''} \dd{\vb{p}'}
        \vb{x}
        \ket{\vb{x}'}
        \underbrace{\braket{\vb{x}'}{p' + \Delta \vb{p}'}}_{\text{eq 1.264}}
        \underbrace{\braket{p'}{\vb{x}''}}_{\text{eq 1.264}^{*}}
        \braket{\vb{x}''}{\alpha}
        \\
        &&&=
        \iiint \dd{\vb{x}'} \dd{\vb{x}''} \dd{\vb{p}'}
        \vb{x}
        \ket{\vb{x}'}
        \underbrace{\left(\frac{1}{2\pi\hbar}\right)^3}_{\text{3 dimensions}}
        \exp(\frac{i(\vb{p}' + \Delta \vb{p}')\cdot \vb{x}'}{\hbar})
        \exp(\frac{-i(\vb{p}') \cdot \vb{x}''}{\hbar})
        \braket{\vb{x}''}{\alpha}
        \\
        &&&=
        \iiint \dd{\vb{x}'} \dd{\vb{x}''} \dd{\vb{p}'}
        \vb{x}
        \ket{\vb{x}'}
        \left(
        \left(\frac{1}{2\pi\hbar}\right)^3
        \exp(\frac{i(\vb{p}' \cdot (\vb{x}'-\vb{x}'') + \Delta \vb{p}' \cdot \vb{x}')}{\hbar})
        \right)
        \braket{\vb{x}''}{\alpha}
        \\
      \end{alignedat}
    \end{equation}

    Hang on a minute, oh wait, Heisenberg was German, so I guess it
    would be Ein Minuten, bitte!\footnote{Here's to you, Eddie
    Izzard.}  That exponential expression looks familiar doesn't it.
    Take a look above at equation \inref{theKey}.  So, what happens if
    we try to isolate that form of it.  Let's pull in another
    handy-dandy identity from the book.

    \begin{equation}
      \tag{1.263}
      \begin{split}
        \delta(x' - x'')
        &= \abs{N}^2 \int \dd{p'} \exp[\frac{ip'(x' - x'')}{\hbar}]\\
        &= 2\pi\hbar\abs{N^2}\delta(x' - x'')
      \end{split}
    \end{equation}

    If you look a couple of lines above there in the book, you'll see
    the derivation which should make it immediately
    obvious.\footnote{If not, drop the class... or... submit a pull
    request to make it more clear.}  Adjusting that equation to
    account for 3 dimensions ($\dd{p'} \rightarrow \dd{\vb{p}'}$ and
    $2\pi\hbar \rightarrow (2\pi\hbar)^3$) then substituting it into
    our expression above

    \begin{equation}
      \begin{alignedat}{2}
        && \vb{x}\mathscr{B}(\Delta \vb{p}')\ket{\alpha}
        &=
        \iiint \dd{\vb{x}'} \dd{\vb{x}''} \dd{\vb{p}'}
        \vb{x}
        \ket{\vb{x}'}
        \left(
        \left(\frac{1}{2\pi\hbar}\right)^3
        \exp(\frac{i(\vb{p}' \cdot (\vb{x}'-\vb{x}'') + \Delta \vb{p}'\vb{x}')}{\hbar})
        \right)
        \braket{\vb{x}''}{\alpha}
        \\
        &&&=
        \int \dd{\vb{x}'}
        \vb{x}
        \exp(\frac{i\Delta \vb{p}' \cdot \vb{x}'}{\hbar})
        \dyad{\vb{x}'}{\vb{x}'}
        \ket{\alpha}
        \\
      \end{alignedat}
    \end{equation}

    Note that when we pulled out the $\delta$ function, we also
    removed the integral over $p'$.  If you'll note, the equality
    involves that integral so that's how we removed it.  Finally, we
    need to get rid of that pesky $x'$ so that we can eliminate our
    final integral.  Thankfully, if you're in operator-land, you can
    replace that variable with the operator itself.

    \begin{equation}
      \begin{alignedat}{2}
        && \vb{x}\mathscr{B}(\Delta \vb{p}')\ket{\alpha}
        &=
        \int \dd{\vb{x}'}
        \vb{x}
        \exp(\frac{i\Delta \vb{p}' \cdot \vb{x}'}{\hbar})
        \dyad{\vb{x}'}{\vb{x}'}
        \ket{\alpha}
        \\
        &&&=
        \vb{x}
        \exp(\frac{i\Delta \vb{p}' \cdot \vb{x}}{\hbar})
        \ket{\alpha}
        \\
      \end{alignedat}
    \end{equation}

    So, in the end, we didn't need the commutator or the $\vb{x}$
    operator at all did we?  It's tempting (in fact, I \emph{did} try
    this and was \emph{rudely} reminded that I was on crack) to assume
    that if $AB = AC$ then $B = C$.  Unfortunately, it doesn't work
    that way (just consider something like $Ax = Ay$ when $A = 0$).
    To be totally rigorous, we'd have to apply $\vb{x}^-1$ on the left
    on both sides.  Without getting into that mess, it's easier just
    to note that all the above derivation holds true if you just
    remove the $\vb{x}$ entirely.  Putting it all together by
    referencing equation \inref{theKey} again, we see that

    \begin{equation}
      \inlabel{solidBooster}
      \mathscr{B}(\dd{\vb{p}'}) = 1 + \frac{i\vb{x} \cdot \dd{p}'}{\hbar}
    \end{equation}
  \end{answerpart}

  \begin{answerpart}{\texorpdfstring{Make it \emph{Just} So}{Make it Just So}}
    \begin{itemize}
    \item \textbf{Inverse/Unitary:} See equation 1.203
      ($\mathscr{J}^\dagger\mathscr{J} \approx 1$)

    \item \textbf{Associative:} See equation 1.204
      ($\mathscr{J}(dp')\mathscr{J}(dp'') = \mathscr{J}(dp' + dp'')$).
    \end{itemize}
  \end{answerpart}

  \begin{answerpart}{Dimensional Analysis (no, really)}
    It has the same dimensionless dimensions as the $\mathscr{J}$
    operator.
  \end{answerpart}

  \begin{answerpart}{The Matrix Has [Your Operator]}

    Heh, this is the last part of the last problem for me.  I
    \emph{had} this in the notes section because I felt like it needed
    to be listed somwehere but I didn't see a good place for it.
    Turns out I \emph{do} have a good place for it.

    \begin{equation}
      \tag{1.247}
      \begin{split}
        \left(1 - \frac{ip\Delta x'}{\hbar}\right)
        &=
        \int \dd{x'}
        \mathscr{J}(\Delta x')\ket{x'}\braket{x'}{\alpha}
        \\
        &=
        \int \dd{x'}
        \ket{x' + \Delta x'}\braket{x'}{\alpha}
        \\
        &=
        \int \dd{x'}
        \ket{x'}\braket{x' -  \Delta x'}{\alpha}
        \\
        &=
        \int \dd{x'}
        \ket{x'}
        \left(
        \braket{x'}{\alpha} - \Delta x' \pdv{}{x'}\braket{x'}{\alpha}
        \right)
        \\
      \end{split}
    \end{equation}

    What he does there at the end is important.  That last
    substitution is the result of taking a first-order Taylor series
    which essentially boils down to

    \begin{equation}
      f(x + dx) = f(x) + dx\pdv{}{x}f(x)
    \end{equation}

    Assuming that the function is differentiable, then the principle
    of local linearity holds and the first-order Taylor series is
    rigorous and complete.  This version, of course, does \emph{not}
    hold up under macroscopic translation, so this only works for
    complete differentials.  The analogous equation for $\mathscr{B}$
    becomes

    \begin{equation}
      \begin{split}
        \left(1 + \frac{ix\dd{p'}}{\hbar}\right)\ket{\alpha}
        &=
        \int \dd{p'}
        \mathscr{B}(\dd{p'})\ket{p'}\braket{p'}{\alpha}
        \\
        &=
        \int \dd{p'}
        \ket{p' + \dd{p'}}\braket{p'}{\alpha}
        \\
        &=
        \int \dd{p'}
        \ket{p'}\braket{p' -  \dd{p'}}{\alpha}
        \\
        &=
        \int \dd{p'}
        \ket{p'}
        \left(
        \braket{p'}{\alpha} - \dd{p'} \pdv{}{p'}\braket{p'}{\alpha}
        \right)
        \\
      \end{split}
    \end{equation}

    Moving down one equation we find that

    \begin{equation}
      \begin{split}
        x\ket{\alpha}
        &= \int \dd{p'} x \ket{p'}\braket{p'}{\alpha}\\
        &= \int \dd{p'} \ket{p'}
        \left(i\hbar\pdv{}{p'}
        \braket{p'}{\alpha}
        \right)
        \\
      \end{split}
    \end{equation}

    Acting $\bra{\vb{p}'}$ on the left side we get
    
    \begin{equation}
      \begin{split}
        \mel{\vb{p}'}{\vb{x}}{\alpha}
        &= \int \dd{\vb{p}''} \braket{\vb{p}'}{\vb{p}''}
        \left(i\hbar\pdv{}{\vb{p}''}
        \braket{\vb{p}''}{\alpha}
        \right)
        \\
        &= \int \dd{\vb{p}''}
        \delta(\vb{p}'-\vb{p}'')
        \left(i\hbar\pdv{}{\vb{p}''}
        \braket{\vb{p}''}{\alpha}
        \right)
        \\
        &= 
        i\hbar\pdv{}{\vb{p}'}
        \braket{\vb{p}'}{\alpha}
        \\
      \end{split}
    \end{equation}

  \end{answerpart}

\end{answer}
