\chapter{Foreward to the First Edition}

Yeah, that's right, this damn thing is big enough that it gets its own
foreward.  Go ahead and skip right over it... I \emph{dare} you.

Ahhem... Err...  As a precursor to exploring quantum computation, I
decided to refresh my basics in quantum mechanics so I worked all the
problems in chapter 1 of Sakurai.  Doing so now with the benefit of
many years in industry yielded this solutions manual.  I hope it
brings you as much pain as it did me.

I tried to address a few deficiencies from my undergrad career as I
went through these exercises.  To help me along the way, a friend of
mine gave me the very best piece of advice that I have ever received
in education: view it as trade school -- you're learning the trade of
being a physicist.  It's not reasonable for us to have to re-derive
everything and even if your goal is to learn the deeper meanings of
things you'll require proficiency with the \acp{ttp} of the trade.  So
I try pretty hard to help the reader stand on the shoulders of the
proverbial giants.  There are a \emph{lot} of tools and I spent a lot
of time just practicing with them... and sometimes breaking one... I
promise I'll buy you a new one.  This kind of trade-shcool approach
was incredibly effective, especially when coupled with an
infinite-capacity forum-post/textbook search-engine in the form of a
\ac{llm}.  After all, you don't learn physics by banging your head
against an integral that everyone else has already solved because they
know ``the trick''.

Speaking of \acp{llm}, going back through these problems I can't help
but notice that undergrad in the oughties doomed many students to
failure while simultaneously relegating others to an unimaginative
future.  In so many cases (check out \outref{1}{24}{theQuestion}) the
\emph{cool} or even the natural way to work a problem is pretty
different than what the author imagines.  It's not that they were
doing a ``bad'' job, so much as they didn't have a better approach
available.  Sometimes the cool way requires tools that they haven't
taught, or it takes time that you don't have, or ...  However, prior
teaching methodologies lacked a tool that we have available to us
today: the \ac{llm}.  Without that tool (which, like most tools,
carries significant risk), the student is dependent upon a collection
of friends, \acp{ta}, the library, coffee, and luck which (at least
when I went through undergrad) seemed to have restricted many of us to
working the problem ``the right way''.

So, if I used an \ac{llm}, did I really \emph{solve} the problems
myself?  That's honestly a question I'm truly worried about.
Unfortunately, I'm doing this almost entirely unsupported.  I have no
study group, \ac{ta}, or even so much as a pen-pal to work through
these with.  Left to my own devices, my solutions would have been
\emph{vastly} less interesting.  There are integrals in the Ice Pick
problem (\outref{1}{24}{theQuestion}) that I would not have been able
to take on my own.  I went back through my prob stats book from
undergrad and even knowing what to look for I would \emph{not} have
made the connection to $\chi^2$.\footnote{In fairness, I have recently
come to the conclusion that I think the Hogg and Tanis book sucks and
have since ordered Jaynes.}  Is it OK to use an integral table?  What
about Wolfram Alpha?  What about a calculator?  It's going to be
years, if not decades, before we know the consequences on human
cognition and learning and creativity of heavy use of \acp{llm}.  To
guard against these hypothesized (and in some cases observed)
failure-modes, I worked quite hard to solve everything on my own and
use the \ac{llm} largely to check my mathematical rigor and every now
and then to provide a hint.  In exactly one case, specifically the
``standard'' (read: ``lame'') way of solving
\outref{1}{34}{theAnswer}, I used the method that the \ac{llm}
recommended.  That was included because I figure I should include the
``standard'' solution in all of the questions, which I do in all
problems though I usually just stumble across it while doing it
the... umm... cool way.

I tried to keep the material fun to read, and to provide enough level
of detail that ensures everyone can keep up.  I uh... I also may have
gone a little overboard on the Ice Pick problem...  You'll see...  I
show you many of the dead-ends that I explored and traps where it's
easy to make a mistake and I try not to be shy about calling myself a
dumbass... don't worry... I'm sure you'll agree with me before too
long.

Jocosity aside, I sincerely hope that this guide helps you in your
journeys... unless you're a Krasnov supporter... in which case I have
a bridge to sell you and would recommend you drop out of your physics
curriculum and get your real estate license.

Sarcastically,

Harrison
